Community-Conditioned Language Models

### 2021-06-11 paper/paper.tex
fixe

\begin{figure*}[t]
    \centering
  \begin{tikzpicture}
    \begin{groupplot}[%
      group style={
        group size=2 by 1,
        horizontal sep=0pt,
      },
      xmin=-1, xmax=1,
      ymin=-1, ymax=1,
      xtick={-0.5,0.5}, ytick={-0.5,0.5},
      axis x line=middle,
      axis y line=middle,
      axis line style={(-)},
      axis on top=true,
      width=0.55\textwidth,
      height=0.55\textwidth,
      scatter/classes={
        0={mark=x, blue},
        1={mark=+, orange},
        2={mark=o, green},
        3={mark=triangle, gray},
        4={mark=star, magenta},
        5={mark=diamond, red}
      },
      ]
      \nextgroupplot[
        %xlabel=$U_0$, ylabel=$U_1$,
        legend cell align=left,
        legend style={font=\tiny},
        legend entries = {
          offmychest confession relationships relationship\_advice SuicideWatch, 
          TrueReddit China europe nyc socialism,
          frugalmalefashion running MechanicAdvice personalfinance Flipping,
          darksouls skyrimmods dragonage Xcom MonsterHunter,
          amiugly Rateme ladybonersgw SchoolIdolFestival GoneWildPlus,
          facepalm CrappyDesign mildlyinfuriating cringepics oddlysatisfying,
        },
        %legend pos=outer south east
        legend to name=pcalegend
      ]
      \addplot[%
        scatter, only marks,
        mark options={thick, scale=0.75},
       scatter src=explicit symbolic,
        ] table [x={web-PCA0}, y={web-PCA1}, meta={web-cluster}] {floats/comm.csv};
      \nextgroupplot[
      %xlabel=$V_0$, ylabel=$V_0$
      ]
      \addplot[%
        scatter, only marks,
        mark options={thick, scale=0.75},
       scatter src=explicit symbolic,
        ] table [x={lstm-3-1-PCA0}, y={lstm-3-1-PCA1}, meta={web-cluster}] {floats/comm.csv};
    \end{groupplot}
  \end{tikzpicture}
  \captionof{figure}{First two components of the aligned social (top) and linguistic (bottom) embeddings,
    where the lingusitic embedding is taken from the LTSM with $l_c=1$.
    Correlation between these directions is given by $\sigma_0 = 53.4$ and $\sigma_1 = 35.6$.
    Colors are assigned by k-means clustering of the social embedding. The legend shows the
    closest 5 communites to each cluster centroid.}
  \label{fig:pca-aligned}
\end{figure*}

>>>>

\begin{figure*}[t]
    \centering
  \begin{tikzpicture}
    \begin{groupplot}[%
      group style={
        group size=2 by 1,
        horizontal sep=0pt,
      },
      xmin=-1, xmax=1,
      ymin=-1, ymax=1,
      xtick={-0.5,0.5}, ytick={-0.5,0.5},
      axis x line=middle,
      axis y line=middle,
      axis line style={(-)},
      axis on top=true,
      width=0.55\textwidth,
      height=0.55\textwidth,
      scatter/classes={
        0={mark=x, blue},
        1={mark=+, orange},
        2={mark=o, green},
        3={mark=triangle, gray},
        4={mark=star, magenta},
        5={mark=diamond, red}
      },
      ]
      \nextgroupplot[
        %xlabel=$U_0$, ylabel=$U_1$,
        legend cell align=left,
        legend style={font=\tiny},
        legend entries = {
          offmychest confession relationships relationship\_advice SuicideWatch, 
          TrueReddit China europe nyc socialism,
          frugalmalefashion running MechanicAdvice personalfinance Flipping,
          darksouls skyrimmods dragonage Xcom MonsterHunter,
          amiugly Rateme ladybonersgw SchoolIdolFestival GoneWildPlus,
          facepalm CrappyDesign mildlyinfuriating cringepics oddlysatisfying,
        },
        %legend pos=outer south east
        legend to name=pcalegend
      ]
      \addplot[%
        scatter, only marks,
        mark options={thick, scale=0.75},
       scatter src=explicit symbolic,
        ] table [x={web-PCA0}, y={web-PCA1}, meta={web-cluster}] {floats/comm.csv};
      \nextgroupplot[
      %xlabel=$V_0$, ylabel=$V_0$
      ]
      \addplot[%
        scatter, only marks,
        mark options={thick, scale=0.75},
       scatter src=explicit symbolic,
        ] table [x={lstm-3-1-PCA0}, y={lstm-3-1-PCA1}, meta={web-cluster}] {floats/comm.csv};
    \end{groupplot}
  \end{tikzpicture}
  \captionof{figure}{First two components of the aligned social (left) and linguistic (right) embeddings,
    where the lingusitic embedding is taken from the LTSM with $l_c=1$.
    Correlation between these directions is given by $\sigma_0 = 53.4$ and $\sigma_1 = 35.6$.
    Colors are assigned by k-means clustering of the social embedding.
    % The legend shows the closest 5 communites to each cluster centroid.
    % JP: commented out this sentence which does not seem to refer to something visible.
    % JP: If the legend shows in the supplementary material, then the whole figure should be repeated there.

  }
  \label{fig:pca-aligned}
\end{figure*}
